Motorcycle Acceleration example

### 2018-11-06 analysis/motorcycle.Rmd
wflow_publish("motorcycle.Rmd")

And in this next plot, we compare the SMASH estimates (orange line)
against the the mean estimates obtained by TI thresholding (dark blue
line), and TI thresholding when the variances have been estimated by
SMASH (dotted green line).

@@

The TI thresholding estimate and the SMASH estimate with homoskedastic
variances both show notable artifacts. When the TI thresholding method
is provided with the SMASH variance estimates, the mean signal is much
more smooth.

>>>>

And in this next plot, we compare the SMASH estimates (the orange
line) against the the mean estimates obtained by TI thresholding (dark
blue line), and TI thresholding when the variances have been estimated
by SMASH (dotted green line).

@@

The TI thresholding estimate and the SMASH estimate with homoskedastic
variances both show notable artifacts. When the TI thresholding method
is provided with the SMASH variance estimate, the mean signal is
substantially smoother.
